Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-14 paper2_JNLS/Referee Reports/Ref1Response/Ref1.tex
NM

\begin{itemize}
\item Thank you for bringing this very relevant reference to our attention. We included this reference and, in addition, have found another reference, Onorato \& Suret 2016, which has analysis specific to KdV. We have now included a discussion of these works, including similarities and differences with our analysis. In particular, note that both of these references considered only uniform depth, whereas, since our work considers variable depth, there must be a formula linking the two ---  the statistical matching condition. See the passage at the end of Section 4.4:

@@

\noindent
\comment{
3. From the experimental point of view, have the authors considered corrections due to the second-order of the Stokes series? When the nonlinearity is important, the bound-modes impact on the skewness may be non-negligible. Is it possible to filter out such corrections in the experimental signal and then compare with the theory? May this explain why the ADC skewness jump is so much larger in the experiment than in the theory?
}

\begin{itemize}
\item
\end{itemize}

>>>>

\begin{itemize}
\item Thank you for bringing this very relevant reference to our attention. We included this reference and, in addition, have found another reference, Onorato \& Suret 2016, which has analysis specific to KdV. We have now included a discussion of these works, including similarities and differences with our analysis. In particular, note that both of these references considered only uniform depth, whereas, since our work considers variable depth, it must account for the transfer of information from one depth to another. This link is provided by the statistical matching condition, which is the key to derive equation (53). See the passage at the end of Section 4.4:

@@

\noindent
\comment{
3. From the experimental point of view, have the authors considered corrections due to the second-order of the Stokes series? When the nonlinearity is important, the bound-modes impact on the skewness may be non-negligible. Is it possible to filter out such corrections in the experimental signal and then compare with the theory? May this explain why the ADC skewness jump is so much larger in the experiment than in the theory?
}
\begin{itemize}
\item Thank you for these suggestions. First, we point out the the skewness jump is {\em not} larger in the experiments than in the theory (we are unsure where the referee got that notion). Rather, provided that the inverse temperature is chosen suitably, the skewness jump is the same across experiments and theory. Perhaps, the referee is referring to the decay of the skewness further downstream of the ADC that appears in the experiments but not the theory. We attribute that behavior to dissipative effects (contact lines, wave breaking, and viscosity) which are unavoidable in the experiments, but are not present in the TKdV theory (which is inviscid, does not permit breaking, and does not account for contact lines with the sidewalls). Please see Bolles et al.~2019 for a more detailed discussion of dissipative effects in the experiments.

It is conceivable that bound modes could contribute somewhat to the downstream skewness, but we point out that we went to great lengths in the experiments to mitigate the effects of bound modes. In particular, we installed a wave dampener at the far end of the tank, which, after making efforts to optimize our design, we found successful eliminates 90\% of reflections from the far end. See again Bolles et al.~2019 for even more details. It is possible that reflections could be controlled to an even greater degree through electronic feedback systems, such as those present in the Hydrodynamics laboratory facilities at Imperial College of London, but we leave that for future work. It is also conceivable that one could create a data processing method to attempt to filter out the bound modes, but seeing as our theory successful captures the observed skewness transitions, we prefer to avoid the possible ambiguities and uncertainties introduced by an extra layer of data manipulation. 
This is not to say that there is anything wrong with filtering data, it is simply a philosophical position: we aim to develop a parsimonious theory that explains and predicts the experimental data in its raw form, or as close to that as possible.
\end{itemize}
